A thesis draft

### 2018-11-19 res/sections/08-Background.tex
Reward virtualization and network virtualization adn add references

\section{Virtualization}
Cloud computing is now a leading-edge Internet technology and the virtualization
technology is one of the most important part of cloud computing systems.
Virtualization, in computing, refers to the act of creating a virtual (rather
than an actual) version of something, including but not limited to a virtual
computer hardware platform, operating system (OS), storage device, or computer
network resources. \todo{This part was taken from ``The research and
implementation of cloud computing platform based on docker'' paper, rework it
in a way it doesn't seem to be copied.}

\subsection{Network Virtualization}
%https://s3.amazonaws.com/academia.edu.documents/29016225/cs-2008-25.pdf?AWSAcce
%ssKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1541352965&Signature=On6XJ5daSAmnfJMnNf41f
%BNHFgg%3D&response-content-disposition=inline%3B%20filename%3DA_survey_of_netwo
%r k _virtualization.pdf
Virtualization, in the networking context, refers to the act of combining
hardware, software and functionalities into a virtual network. This abstraction
runs on the top of a physical network in a hyper-visor, decoupling the logical
network from the hardware one. Network virtualization allow multiple,
heterogeneous networks to cohabit, increasing the flexibility and manageability.
%http://www.csc.villanova.edu/~nadi/csc8580/S11/DeeptiNune.pdf
%https://www.sciencedirect.com/science/article/abs/pii/S1389128609003387
The idea of network virtualization came from the decoupling of the role of the
traditional ISP into two different entities: who provides the infrastructure
(InPs) and who provides the services(SPs). In that context it is possible to
aggregate resources, even from different InPs, creating a virtual network,
offering an end-to-end service. Most known instances of NV are \emph{VPNs},
dedicated networks that allows the communication among multiple sites, using
private and secure tunnels, relying on the public network such as Internet.
Other examples of network virtualization are \emph{overlay networks}. They are
logical networks, build on the top of an existing physical network, typically
implemented at the application layer.

>>>>

\section{Virtualization}
Cloud computing is nowadays one of the cutting edge Internet technologies, and
it is possible thanks to virtualization, that allows to isolate applications,
optimizing the utilization of hardware resources and providing more flexibility.
Virtualization, in computing, usually refers to the act of creating a virtual
version of a certain asset, such as virtual computer hardware platform,
operating system (OS), storage device, or computer network
resources~\cite{liu2014research}. Conventional virtualization
(hypervisor-based) uses virtual machines: it provides strong isolation and a
complete operating system~\cite{eder2016hypervisor}. In hypervisor
virtualization every pieces of hardware required to running software is
emulated, and it is common that the hypervisor provides interfaces to access
the real hardware, for instance to access physical devices or to communicate
with the network. However all this functionalities comes to a resource
overhead~\cite{scheepers2014virtualization}Container-based virtualization,
instead, could be a more efficient in certain context, because it does not
emulate the entire computer. A container is seen as an isolate process running
on the host, to which the Linux kernel gives a set of capabilities.

\subsection{Network Virtualization}
%http://www.csc.villanova.edu/~nadi/csc8580/S11/DeeptiNune.pdf
%https://www.sciencedirect.com/science/article/abs/pii/S1389128609003387
Virtualization, in the networking context, refers to the act of combining
hardware, software and functionalities into a virtual network. This abstraction
runs on the top of a physical network in a hyper-visor, decoupling the logical
network from the hardware one. Network virtualization allow multiple,
heterogeneous networks to cohabit, increasing the flexibility and manageability.
The idea of network virtualization came from the decoupling of the role of the
traditional ISP into two different entities: who provides the infrastructure
(InPs) and who provides the services(SPs). In that context it is possible to
aggregate resources, even from different InPs, creating a virtual network,
offering an end-to-end service~\cite{chowdhury2009network}. Most known
instances of NV are \emph{VPNs}, dedicated networks that allows the
communication among multiple sites, using
private and secure tunnels, relying on the public network such as Internet.
Other examples of network virtualization are \emph{overlay networks}. They are
logical networks, build on the top of an existing physical network, typically
implemented at the application layer.
